### 2015-02-03 paper_10_intro.tex
minor update to abstract

    Process mining has also been applied to decision making regarding software 
    upgrades \cite{Genuchten2014}.  Historic and current logs can be 
    processed and evaluated.
    Then small pilot groups can be offered the upgrade, and the new logs will 
    be processed and evaluated. Thus, process mining can be beneficial for new 
    software implementation.  More research needs to be done applying
    process mining to the other process involved with software development,
    such as other documentation, testing, and implementation.

>>>>

    Process mining has also been applied to decision making regarding software 
    upgrades \cite{Genuchten2014}.  Historic and current logs can be 
    processed and evaluated.
    Then small pilot groups can be offered the upgrade, and the new logs will 
    be processed and evaluated. Thus, process mining can be beneficial for new 
    software implementation.  More research needs to be done applying
    process mining to the other processes involved with software development,
    such as other documentation, testing, and implementation.
